% Title: Report LaTex File: Project Overview
% Auther: DC Eksteen
% Student Number: 22623906
% Contact: 22623906@sun.ac.za
% Date: 2022/09/14
% Version: 2.0

\title{
	Development of an Affordable Zwift-Enabled Smart Bicycle Trainer
}
\author{D.\ C.\ Eksteen}{Dylan Charl Eksteen}
\studentnumber{22623906}
\subject{MP 478}{Mechatronic Project 478}
\ReportDescript{Final Report}
\supervisor{Dr.\ G.\ Venter}
\setdate{\month}{\year}


\Objectives{
	\textbullet \space Design and implement a software solution for connecting and interfacing with the Zwift application.\\
	\textbullet \space Design and build an inexpensive bicycle trainer with controllable resistance and smart connectivity.\\
	\textbullet \space Test the accuracy and user experience of the developed smart trainer.
}

\CurrentPractice{
	\textbullet \space Commercial smart trainers that are compatible with Zwift are very expensive and thus inaccessible to many consumers.\\
	\textbullet \space Accessories such as training tyres and additional cassettes also add to the costs of many available trainers.\\
	\textbullet \space There is a shortage of accessible information and resources for enthusiasts to develop their own trainers and supporting platforms.
}

\NewInProject{
	\textbullet \space This project developed a software solution with supporting documentation for connecting and interacting with the Zwift application.\\
	\textbullet \space The project provides an example of developing and implementing a smart trainer using the developed software.\\
	\textbullet \space The demonstrated smart trainer functions similarly to traditional roller trainers. This type of trainer is not commonly found with smart-connectivity features.
}

\ProjectDifference{
	\textbullet \space The developed software solution provides a starting platform for DIY enthusiasts and product developers to create new smart-trainer platforms and applications.\\
	\textbullet \space The demonstrated smart-rollers trainer would allow many consumers to develop and build smart trainers at a more affordable price and with a more robust application.
}

\ProjectRisks{
	\textbullet \space There was a risk of proprietary software or information required to interact with the Zwift application. This was managed and mitigates as the software was developed and tested and proved to have little impact on the project outcome.\\
	\textbullet \space Supply and manufacturing of components during a worldwide supply-chain shortage. Although this inevitably affected the progress of the project, the majority of the concerns were mitigated with good planning and effective use of resources.   
}

\Credits{
	This was an individual project with no assistance from other students. Any external resources that were copied, adopted or otherwise utilised are cited and referenced where relevant.
}

\Continuation{
	NA
}

\ContinuationArrangements{
	\textbullet \space The developed software and electronics schematics will be available on a GitHub repository under an open license available at: \url{https://github.com/TheMechatronic/Skripsie-2022}.\\
	\textbullet \space The hardware development process was thoroughly documented and presented in this report.
}
